---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# wkmesh

<!-- badges: start -->
<!-- badges: end -->

The goal of wkmesh is to explore methods of creating meshes, we might move on from silicate/anglr, but at least we want to avoid dealing with formats, leverage wk/geos, and get a firmer basis for this. 

We triangulate from edges but we don't currently trim holes or maintain identity of input features (use anglr or silicate with sf objects for now). 


## Installation

I wouldn't.  Nothing is exported, mostly I'm just leaving a trail for myself (indexing for meshes can be tricky and I only have informal methods. The main workhorse is {unjoin} and I'd like to expand out why that's so easy to use and how to use other methods). 

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

This is a basic example: 

```{r example}
devtools::load_all()
library(wkmesh)
library(wk)
library(dplyr, warn.conflicts = FALSE)
library(silicate)
g <- wk::as_wkb(minimal_mesh)

system.time({

x <- edges_vctrs(g)
})

system.time({

x <- edges_unjoin(g)
})

# system.time({
#   sc <- SC0(inlandwaters)
# })

#plot(sc)
(el <- edge_linestring(x))


del <- del_edges(x)
names(del)
plot_del(del)


```

We have some informal functions to experiment with. 

```{r draft}

## this is just different methods of unique-fying coordinates to vertices
edges_vctrs(inlandwaters)
edges_unjoin(inlandwaters)

## Delauanay criterion strict, minimal triangle angle 15 degrees
plot_del(del_edges(edges_unjoin(inlandwaters[4, ]), D = T, q = 15))
```


## Code of Conduct
  
Please note that the wkmesh project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/1/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
